A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add EGf description

$\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ is satisfied for a
state $s$ if $f_2$ is satisfied by $s$ or $s$ satisfies $f_1$ and $s$ has a
successor state $t$ such that a path exists starting at $t$ and satisfying
$f_1 \text{\textbf{U}} f_2$. The $\mu$-Calculus representation is defined by
$\mu Q \lbrack f_2 \lor \left( f_1 \land \text{\textbf{EX}} Q \right) \rbrack$~\cite{BURCH90}.\tbr

>>>>

$\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ is satisfied for a
state $s$ if $f_2$ is satisfied by $s$ or $s$ satisfies $f_1$ and $s$ has a
successor state $t$ such that a path exists starting at $t$ and satisfying
$f_1 \text{\textbf{U}} f_2$. The $\mu$-Calculus representation (lfp) is defined by
$\mu Q \lbrack f_2 \lor \left( f_1 \land \text{\textbf{EX}} Q \right) \rbrack$~\cite{BURCH90}.

$\text{\textbf{EG}} f$ is satisfied for a state $s$ if $s$ satisfies $f$ and there
exists a successor state $t$ satisfying $f$ globally. Hence, the equivalent 
gfp representation is
$\nu Q \lbrack f \land \text{\textbf{EX}} Q \rbrack$~\cite{BURCH90}.

\tbr
